Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-02-17 manuscript/manuscript.Rmd
Update manuscript.Rmd

compute_lambda <- function(mu, x, method){
  # Create transformer object.
  transformer <- suppressWarnings(
    power.transform::find_transformation_parameters(
      x = x + mu,
      method = method,
      robust = FALSE,
      shift = FALSE,
      lambda = NULL))

@@

  .compute_lambda <- function(parameter_set){
    # Create transformer object.
    transformer <- suppressWarnings(
      power.transform::find_transformation_parameters(
        x = parameter_set$x,
        method = parameter_set$method,
        robust = parameter_set$robust,
        shift = parameter_set$shift,
        lambda = NULL))

@@

@@

@@

@@

@@

@@

@@

>>>>

compute_lambda <- function(mu, x, method){
  # Create transformer object.
  transformer <- suppressWarnings(
    power.transform::find_transformation_parameters(
      x = x + mu,
      method = method,
      robust = FALSE,
      shift = FALSE,
      lambda = NULL,
      optimiser_control = list("xtol_rel"=1e-3)))

@@

  .compute_lambda <- function(parameter_set){
    # Create transformer object.
    transformer <- suppressWarnings(
      power.transform::find_transformation_parameters(
        x = parameter_set$x,
        method = parameter_set$method,
        robust = parameter_set$robust,
        shift = parameter_set$shift,
        lambda = NULL,
        optimiser_control = list("xtol_rel"=1e-3)))

@@

      for(robustness_source in c("empirical_probability", "transformed", "residual")){

@@

        if(robustness_source == "empirical_probability"){
          def_opt_limits$k1[2] <- 1.0
          def_opt_limits$k2[2] <- 1.0

@@

            fun_args <- list(
              "method" = method,
              "robust" = TRUE,
              "shift" = TRUE,
              "weighting_function" = paste0(robustness_source, "_", robustness_weighting_function),
              "backup_use_default" = FALSE)

@@

            yield(list(
              "name" = paste0(robustness_source, "-", robustness_weighting_function),
              "method" = method,
              "fun_args" = fun_args,
              "opt_args" = list("initial" = opt_init, "limits" = opt_limits)
            ))
          }
        }
      }
    }
  )

@@

    # Custom parser.
    ..outlier_parser <- function(
    x,
    fun_args,
    opt_args
    ){
      # Create transformer.
      transformer <- suppressWarnings(do.call(
        power.transform::find_transformation_parameters,
        args=c(
          list("x" = x$x),
          list("weighting_function_parameters" = opt_args),
          fun_args)))

@@

    } else {
      # Yeo-Johnson.
      lambda_error <- sapply(
        parameter_data,
        function(x) (abs(x$lambda - x$target_lambda_yj)))
    }
    cat(paste0("target: ", mean(lambda_error), "; k1: ", opt_param[1], "; k2: ", opt_param[2], "\n"))
    return(mean(lambda_error))
  }

@@

      h <- nloptr::sbplx(
        x0 = x0,
        fn = ..optimisation_function,
        lower = lower,
        upper = upper,
        control=list("xtol_rel"=1e-2),
        x = data,
        fun_args = experiment$fun_args,
        cl_internal = cl_internal)
